Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-11-25 referee_2.tex
Adding response to major comment 1

    The convergence study is a great addition to the paper. However, the lowest limit explored here (0.625pc) is a factor of roughly 100 larger than the scale on which fragmentation can be seen (compare eg the 1000AU regions, in which several Pop III stars form in work by Stacy+16). I recommend to explicitly state down to which resolution the convergence was tested in Section 2.2.1 and adding these limitations to the "Caveats" section. Instead of single Pop III stars, this paper is a study of the multiplicity of Pop III star formation regions. Please make this clear in the paper. 
\end{referee}
    The lowest limit has been added to section 2.2.1.

    --Added to the caveats

    \jhw{I've add some wording in Sections 2.2.1 and 3.3 about fragmentation and our study being a lower limit on the multiplicity but nothing to the caveats section. I think with these statements, we can argue in the response that changes throughout the text are not needed. Make the changes to the caveats section, and I'll write the rebuttal here.}

>>>>

    The convergence study is a great addition to the paper. However, the lowest limit explored here (0.625pc) is a factor of roughly 100 larger than the scale on which fragmentation can be seen (compare eg the 1000AU regions, in which several Pop III stars form in work by Stacy+16). I recommend to explicitly state down to which resolution the convergence was tested in Section 2.2.1 and adding these limitations to the "Caveats" section. Instead of single Pop III stars, this paper is a study of the multiplicity of Pop III star formation regions. Please make this clear in the paper. 
\end{referee}
    In Section 2.2, we have expanded our description of the convergence study to include the smallest resolution and pointed out that the overdensity formation criterion is similar to a molecular core.  We explicitly state that our results are lower limits on the number of Pop III stars, massive and low-mass, in this section.  Furthermore, we remind the reader about this lower limit in Section 3.3, where we present our results on the stellar multiplicity.  Lastly, we have added a paragraph in the Caveats section (S4.3) about our simulation not resolving fragment below 0.625 pc and emphasize that our work strengthens the case for multiple Pop III stars in each halo, especially considering this limitation.

    That being said, we decided to refer to these star forming regions as ``stars'' throughout the paper because the phrase ``star forming regions'' or something similar would have been too wordy because it is mentioned many times throughout the manuscript and in the figures.  We feel that emphasizing that our results are lower limits on the number of massive Pop III stars is a good compromise.
